---
title: "Exploration Graphs for Variables in Dataframes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic_graphs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(explore)
```

# Basic Exploration Functions  

Different basic explore functions, depending on variable type (numeric or categorical) and variable count (1 or 2), take a dataframe and variable names as input and output interactive plots to illustrate the distribution of one variable or the relationship between multiple variables.

## Exploration of 1 numeric variable  

Given a dataframe and the name of a numeric variable in that dataframe, this function generates interactive plots showing the distribution of that variable.

```{r example}
library(explore)

num_1(iris, Sepal.Length)
```

## Exploration of 2 numeric variables   

Given a dataframe and the names of two numeric variable in that dataframe, this function generates interactive plots showing the distribution of one variable against the other.

```{r}
num_2(iris, Sepal.Length, Sepal.Width)
```

## Exploration of 1 categorical variable  

Generates visualizations for the distribution of one categorical variable.

```{r}
cat_1(iris, Species)
```

## Exploration of 1 numeric variable and 1 categorical variable  

Generates visualizations for the distribution of one numeric variable split by 
one categorical variable and vice versa.

```{r}
num1_cat1(iris, Sepal.Length, Species)
```

## Exploration of 2 numeric variables and 1 categorical variable  
Generates visualizations for the distribution of two numeric variables split by one categorical variable.

```{r}
num2_cat1(iris, Sepal.Length, Sepal.Width, Species)
```

## Exploration of 1 numeric variable and 2 categorical variables  
Generates a visualization for the distribution of two categorical variables based on one numeric variable.

```{r}
# Creating new categorical column in the iris dataset
iris <- iris
random <- c("a", "b", "c")
iris$cat <- sample(random, size = nrow(data), replace = TRUE)

num1_cat2(iris, cat, Sepal.Length, Species)
```




