---
title: "Explore Mapping"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explore Mapping}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(explore)
```

Explore's mapping functions 'explore_points' and 'explore_polygons' aim to help users visualize spatial data efficiently.

### Inspiration 

Mapping in R is hard. Explore mapping functions simplify the steps needed to create tidy and advanced visualizations with point and polygon/multipolygon data. These functions within the explore package are useful for anyone wanting to visualize their raster data simply and efficiently

### Functions

Each function takes a data frame with a 'geometry' column and plots accordingly on to an OpenStreetMap interactive base.

* `explore_points()` visualizes geometry of class 'point' with two visualizations; a point or dot map as well as a heat map that are output into a list.  
```{r}
library(sf)
#import example data for explore_points
point_data <- st_as_sf(st_sample(st_read(system.file("shape/nc.shp", package="sf")), 100))

explore_points(point_data)

```
* `explore_polygons()` visualizes geometry of class 'polygon' or 'multipolygon' in three visualizations; a basic plot of geometric shapes, a classed map, and a gradient map.  Maps are output into a list.

```{r}
#import example data for explore_polygons
polygon_data <- st_read(system.file("shape/nc.shp", package="sf"))

explore_polygons(var_column = "FIPS")$plot_scaled(polygons)

explore_polygons(var_column = "AREA")$plot_gradient(polygons)

explore_polygons()$plot_basic(polygons)

```











