---
title: "Explore Mapping"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explore Mapping}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(explore)
```

Explore's mapping functions 'explore_points' and 'explore_polygons' aim to help users visualize spatial data efficiently.

### Inspiration 

Mapping in R is hard. Explore mapping functions simplify the steps needed to create tidy and advanced visualizations with point and polygon/multipolygon data. These functions within the explore package are useful for anyone wanting to visualize their raster data simply and efficiently

### Functions

Each function takes a data frame with a 'geometry' column and plots accordingly on to an OpenStreetMap interactive base.

* `explore_points()` visualizes geometry of class 'point' with two visualizations; a point or dot map as well as a heat map that are output into a list.  

* `explore_polygons()` visualizes geometry of class 'polygon' or 'multipolygon' in three visualizations; a basic plot of geometric shapes, a classed map, and a gradient map.  Maps are output into a list.

```{r}
#example <- explore_points(points)
```










